---
title: "taskassignement2"
author: "moi"
date: "22/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(rjstat)
library(stringr)
library(dplyr)
library(lubridate)
library(knitr)
library(DT)
library(DataExplorer)
library(ggplot2)
library(tidyr)

```

# Download table

```{r}

url="http://data.ssb.no/api/v0/dataset/95274.json?lang=no"
datanew=GET(url)
str(datanew)
datanewtext=content(datanew,as="text")
datanewparsed=content(datanew,as="parsed")
dataJson=fromJSONstat(datanewtext)
dataJson
str(dataJson)

dataJ=dataJson$`03616: Hotell og liknande overnattingsbedrifter. Kapasitetsutnytting og pris per rom, etter region, m책ned og statistikkvariabel`

url="http://data.ssb.no/api/v0/dataset/95276.json?lang=no"
data2=GET(url)
str(data2)
data2text=content(data2,as="text")
data2parsed=content(data2,as="parsed")
dataJson2=fromJSONstat(data2text)
dataJson2
str(dataJson2)

dataJ2=dataJson2$`03616: Hotell og liknande overnattingsbedrifter. Kapasitetsutnytting og pris per rom, etter region, m책ned og statistikkvariabel`


```
# The names of the four columns in english
```{r}

dataJ=dataJ%>%rename("Date"="m책ned" ,"Variables"="statistikkvariabel")
dataJ2=dataJ2%>%rename("Date"="m책ned" ,"Variables"="statistikkvariabel")

```

# Change the Date Format
```{r}

dataJ$Date =as.character(dataJ$Date)
dataJ$Date = str_replace(dataJ$Date,"M", "01")
dataJ$Date = as.Date(dataJ$Date, format="%Y%d%m")

dataJ2$Date =as.character(dataJ2$Date)
dataJ2$Date = str_replace(dataJ2$Date,"M", "01")
dataJ2$Date =as.Date(dataJ2$Date, format="%Y%d%m")

```

# Recode the Norwegian labels into English.

```{r}

dataJ$Variables <- recode(dataJ$Variables, 
       "Kapasitetsutnytting av senger (prosent)" = "Beds percentage capacity utilization",
       "Kapasitetsutnytting av rom (prosent)" = "Rooms percentage capacity utilization",
       "Pris per rom (kr)" = "Price per room (kr)")

dataJ2$Variables <- recode(dataJ2$Variables, 
       "Kapasitetsutnytting av senger (prosent)" = "Beds percentage capacity utilization",
       "Kapasitetsutnytting av rom (prosent)" = "Rooms percentage capacity utilization",
       "Pris per rom (kr)" = "Price per room (kr)")

```


# Merge the two dataframes

```{r}

dataJ <- mutate(dataJ, df = "dataJ")
dataJ2<- mutate(dataJ2, df = "dataJ2")
DATA <- rbind(dataJ, dataJ2)

```

# Calculate the difference between county average room price and the national average room price per month. 

```{r}

dataJ$month = format(dataJ$Date,"%m")
dataJ2$month = format(dataJ2$Date,"%m")

dataJ_average = dataJ %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(month) %>% 
                summarise(mean_priceroom_dataJ = mean(value))


dataJ2_average = dataJ2 %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(month) %>% 
                summarise(mean_priceroom_dataJ2 = mean(value))



AVERAGE_PRICE= left_join(dataJ_average,dataJ2_average,by="month")

AVERAGE_PRICE$diff = AVERAGE_PRICE$mean_priceroom_dataJ-AVERAGE_PRICE$mean_priceroom_dataJ2

plot(x= AVERAGE_PRICE$month, y = AVERAGE_PRICE$diff, type = "l", col="red",
     xlab="month", 
     ylab="Room price difference", 
     main="Difference of average room price")


```

# What county (on average) has the highest positive and negative difference in price?


```{r, results="asis"}

dataJ_average_mr = dataJ %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(month,region) %>% 
                summarise(mean_priceroom_dataJ = mean(value))


dataJ2_average_mr = dataJ2 %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(month,region) %>% 
                summarise(mean_priceroom_dataJ2 = mean(value))


dataJ_average_mr$diff = dataJ_average_mr $mean_priceroom_dataJ -dataJ2_average_mr$mean_priceroom_dataJ2 

max_diff = str_sub(dataJ_average_mr[dataJ_average_mr$diff==max(dataJ_average_mr$diff),1])
max_month = as.Date(paste0("2000-",max_diff,"-1"), format="%Y-%m-%d") 
max_month_format = month(max_month, label=TRUE, abbr=FALSE)

max_region = str_sub(dataJ_average_mr[dataJ_average_mr$diff==max(dataJ_average_mr$diff),2])

min_diff = str_sub(dataJ_average_mr[dataJ_average_mr$diff==min(dataJ_average_mr$diff),1])
min_month = as.Date(paste0("2000-",min_diff,"-1"), format="%Y-%m-%d") 
min_month_format = month(min_month, label=TRUE, abbr=FALSE)

min_region = str_sub(dataJ_average_mr[dataJ_average_mr$diff == min(dataJ_average_mr$diff),2])

datatable(dataJ_average_mr)
```


**`r max_region` is the county with the highest positive difference in price, it happens for the month of `r max_month_format` whereas `r min_region` is the county with the highest negative difference in price, it happens for the month of `r min_month_format`**


# Do the calculations above per county and per year.

```{r}

dataJ$year= format(dataJ$Date,"%Y")
dataJ2$year = format(dataJ2$Date,"%Y")
DATA$year=format(DATA$Date,"%Y")


dataJ_AY= dataJ %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(year) %>% 
                summarise(mean_priceroom_dataJ = mean(value))


dataJ2_AY= dataJ2 %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(year) %>% 
                summarise(mean_priceroom_dataJ2 = mean(value))

fusion=left_join(dataJ_AY,dataJ2_AY,by="year")
fusion$Diff=fusion$mean_priceroom_dataJ-fusion$mean_priceroom_dataJ2

```

# Make a plot ofthe price difference for Troms county from 1999 until today.

```{r}

plot(x= fusion$year[8:28], y = fusion$Diff[8:28], type = "l", col="purple", 
     xlab="Year", 
     ylab="Room price difference", 
     main="the monthly price difference for Troms county from 1999 until today")


```

# Identify the year and county with the highest positive and negative difference.

```{r, results="asis"}


dataJ_AYR= dataJ %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(year,region) %>% 
                summarise(mean_priceroom_dataJ = mean(value))

dataJ2_AYR= dataJ2 %>% 
                filter(value != 0.0, Variables == "Price per room (kr)") %>% 
                group_by(year,region) %>% 
                summarise(mean_priceroom_dataJ2 = mean(value))

```


```{r, results="asis"}

dataJ_AYR$diff = dataJ_AYR$mean_priceroom_dataJ - dataJ2_AYR$mean_priceroom_dataJ2
dataJ_AYR =dataJ_AYR %>% drop_na()

max_year =str_sub(dataJ_AYR[dataJ_AYR$diff== max(dataJ_AYR$diff),1])
min_year =str_sub(dataJ_AYR[dataJ_AYR$diff== min(dataJ_AYR$diff),1])

max_diff =str_sub(dataJ_AYR[dataJ_AYR$diff== max(dataJ_AYR$diff),2])
min_diff =str_sub(dataJ_AYR[dataJ_AYR$diff== min(dataJ_AYR$diff),2])

datatable(dataJ_AYR)

```


**`r max_diff` is the county with the highest positive difference in price, it happens for the year of `r max_year` whereas `r min_diff` is the county with the highest negative difference in price, it happens for the year of `r min_year`**


# Make a plot of the monthly price difference for Troms county from 1999 until today.

```{r}

tromsJ = dataJ%>% filter( Date >= "1999-01-01", value != 0.0, Variables == "Price per room (kr)")

tromsJ2= dataJ2  %>% filter( Date >= "1999-01-01", value != 0.0, Variables == "Price per room (kr)")

tromsJ$diff= tromsJ$value - tromsJ2$value

plot(x= tromsJ$Date, y = tromsJ$diff, type = "p",
     xlab="Month", 
     ylab="Room price difference", 
     main="the monthly price difference for Troms county from 1999 until today")

```



# Per county, is there any relationship (correlation) between room capacity and price since January 2010?


```{r}

C1 <- DATA %>% 
  filter(Variables == "Price per room (kr)") %>%
  subset(Date>= "2010-01-01" & Date <= Sys.Date()) %>% 
  rename(price = value) %>% 
  select(., -c(Variables))
 
C2<- DATA %>% 
  filter(Variables == "Rooms percentage capacity utilization") %>%
  subset(Date>= "2010-01-01" & Date <= Sys.Date()) %>% 
  rename(rooms_capacity = value) %>% 
  select(., -c(Variables))

cor.test(C1$price, C2$rooms_capacity)
```

The pvalue of the correlation is less than 10% so we can conclude that we don't have a correlation between the price and the capacity of the room