---
title: "Task 4"
author: "moi"
date: "31/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(mosaic)
library()
```

## Dowloads DATA

```{r}
```
1: For the last 3 months of 2017, calculate the total Sales by month, for Region 1 and Region 9 in the Customer_Segment, Corporate and Consumer. This output is Table 1.

2: Make a plot of the monthly total Sales in Region 1 and Region 13 in 2015, 2016 and 2017. This output is Figure 1.

3: In Figure 1, identify the months where the total Sales in Region 13 is greater than the total Sales in Region 1. This output is Table 2.

4: Find average Profit per Customer_Segment and Product_Category in 2017, for all regions except Region 3, 5 and 8. What segment produced the highest average profit? This output is Table 3.

5: You are asked to estimate a SARIMA model on the aggregated monthly Order_Quantity in the Customer_Segment; Small Business and Product_Category; Office Supplies. The SARIMA model contains the following parameters: